---
title: "Texas Pop Analysis"
author: "joshua Brikowski"
date: "July 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Texas Population, 2016 (Projections) info
This data was taken from https://www.dshs.texas.gov/chs/popdat/ST2016p.shtm. it had 8 cols labeld FIPS |	County |	County Name |	Total |	Anglo |	Black |	Hispanic | Other. This data represents the enthinic distinction for each county. 
NOTE:
-2010 contained actual census data thus is not dependent on any predictions.

-Removed the FIPS col since it was just alternateing odd numbers and essentually represented the same thing as the County.

```{r cars, echo=FALSE}
library(ggplot2)
library(reshape2)
library(readxl)
library(gridExtra)
tp2017 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2017", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2016 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2016", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))

tp2015 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2015", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2014 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2014", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2013 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2013", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2012 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2012", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2011 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2011", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2010 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2010", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
```
##Helper Functions
-countypop <- gives 2010-2017 data on county

-plotAll <- plots all of county stats on graph
-ggplotRegression <- plots points with regression line






```{r anderson, echo=FALSE}
countypop <- function(countyName){
  POP <- c(tp2010$Total[which(tp2010$`County Name` == countyName)],
  tp2011$Total[which(tp2011$`County Name` == countyName)],
  tp2012$Total[which(tp2012$`County Name` == countyName)],
  tp2013$Total[which(tp2013$`County Name` == countyName)],
  tp2014$Total[which(tp2014$`County Name` == countyName)],
  tp2015$Total[which(tp2015$`County Name` == countyName)],
  tp2016$Total[which(tp2016$`County Name` == countyName)],
  tp2017$Total[which(tp2017$`County Name` == countyName)])
  
  Anglo <- c(tp2010$Anglo[which(tp2010$`County Name` == countyName)],
  tp2011$Anglo[which(tp2011$`County Name` == countyName)],
  tp2012$Anglo[which(tp2012$`County Name` == countyName)],
  tp2013$Anglo[which(tp2013$`County Name` == countyName)],
  tp2014$Anglo[which(tp2014$`County Name` == countyName)],
  tp2015$Anglo[which(tp2015$`County Name` == countyName)],
  tp2016$Anglo[which(tp2016$`County Name` == countyName)],
  tp2017$Anglo[which(tp2017$`County Name` == countyName)])

  Black <- c(tp2010$Black[which(tp2010$`County Name` == countyName)],
  tp2011$Black[which(tp2011$`County Name` == countyName)],
  tp2012$Black[which(tp2012$`County Name` == countyName)],
  tp2013$Black[which(tp2013$`County Name` == countyName)],
  tp2014$Black[which(tp2014$`County Name` == countyName)],
  tp2015$Black[which(tp2015$`County Name` == countyName)],
  tp2016$Black[which(tp2016$`County Name` == countyName)],
  tp2017$Black[which(tp2017$`County Name` == countyName)])

  Hispanic <- c(tp2010$Hispanic[which(tp2010$`County Name` == countyName)],
  tp2011$Hispanic[which(tp2011$`County Name` == countyName)],
  tp2012$Hispanic[which(tp2012$`County Name` == countyName)],
  tp2013$Hispanic[which(tp2013$`County Name` == countyName)],
  tp2014$Hispanic[which(tp2014$`County Name` == countyName)],
  tp2015$Hispanic[which(tp2015$`County Name` == countyName)],
  tp2016$Hispanic[which(tp2016$`County Name` == countyName)],
  tp2017$Hispanic[which(tp2017$`County Name` == countyName)])

  Other <- c(tp2010$Other[which(tp2010$`County Name` == countyName)],
  tp2011$Other[which(tp2011$`County Name` == countyName)],
  tp2012$Other[which(tp2012$`County Name` == countyName)],
  tp2013$Other[which(tp2013$`County Name` == countyName)],
  tp2014$Other[which(tp2014$`County Name` == countyName)],
  tp2015$Other[which(tp2015$`County Name` == countyName)],
  tp2016$Other[which(tp2016$`County Name` == countyName)],
  tp2017$Other[which(tp2017$`County Name` == countyName)])


  year = 2010:2017
  
  
  return(data.frame(year,POP,Anglo,Black,Hispanic,Other)) 
  
}


plotAll <- function(df,name){
  d <- melt(df, id.vars="year")
  # Everything on the same plot
  ggplot(d, aes(year,value, col=variable)) + 
  geom_point() + 
  stat_smooth() +
  labs(title=name, x="Year", y="Population")
}

ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}


```


## Anderson county growth over 10-17

```{r Anderson, echo=FALSE}
AndersonDF <- countypop('Anderson')

summary(AndersonDF)
plotAll(AndersonDF,'Anderson')

# Separate plots
#ggplot(d, aes(year,value)) + 
#  geom_point() + 
#  stat_smooth() +
#  facet_wrap(~variable)
```

##County with largest change
After querrying the data we find harris county to have the largest growth of any county. This is probably atributed to it being one of the largest. its biggest demographic growth is hispanic.

```{r bigestChange, fig.width = 10, fig.height=4, echo=FALSE}
largestChangeCounty = 1
countyNum = 1
while(countyNum <nrow(tp2010)){
  if((tp2017$Total[countyNum]-tp2010$Total[countyNum]) > (tp2017$Total[largestChangeCounty]-tp2010$Total[largestChangeCounty])){
    largestChangeCounty = countyNum
  }
  countyNum = countyNum +1
}




largestName <- tp2010$`County Name`[which(tp2010$County == largestChangeCounty)]
DF101 <- countypop(largestName)


p1 <- plotAll(DF101,largestName)

p2 <- plotAll(DF101[,-2], 'Harris Demographics')
p3 <- plotAll(DF101[,c(1,5)], 'Harris Hispanic')
p4 <- plotAll(DF101[,c(1,3)], 'Harris Anglo')
grid.arrange(p1, p2,p3,p4, ncol=2)


```



##predict the pop growth for Texas

Here we can see a regression line fitted to the population data points. i also predict the population in 2025.

```{r predictHarris, echo=FALSE, fig.width=15,fig.height=4}
my.list <- list(tp2010, tp2011,tp2012,tp2013,tp2014,tp2015,tp2016,tp2017)
year = 2010:2017
population = c(sum(tp2010$Total),sum(tp2011$Total),sum(tp2012$Total),sum(tp2013$Total),sum(tp2014$Total),sum(tp2015$Total),sum(tp2016$Total),sum(tp2017$Total))
texaspop <- data.frame(year,population)

lm1 <- lm(population~year, data=texaspop)
p1 = plotAll(texaspop,"Texas")
summary(lm1)

p2 = ggplotRegression(lm1)


grid.arrange(p1, p2, ncol=2)

```







