---
title: "Texas Pop Analysis"
author: "joshua Brikowski"
date: "July 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## exas Population, 2016 (Projections) info
this data was taken from https://www.dshs.texas.gov/chs/popdat/ST2016p.shtm. it had 8 cols labeld FIPS |	County |	County Name |	Total |	Anglo |	Black |	Hispanic | Other.
this data represents the enthinic distinction for each county. i have gotten the XLS sheets for 2010-2017.

i copyed and paisted the data directly from the website. annoyingly there is not xls or csv easaly findable on thsi website.

for 2011 and 2012 i had issues converting to xls. just chaneg to plain text then it wall copy over.

2010 contained actual census data thus is not dependent on any predictions.

i remived the FIPS col since it was just alternateing odd numbers and essentually represented the same thing as the County.

```{r cars}
library(ggplot2)
library(reshape2)
library(readxl)
library(gridExtra)
tp2017 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2017", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2016 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2016", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))

tp2015 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2015", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2014 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2014", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2013 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2013", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2012 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2012", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2011 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2011", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
tp2010 <- read_excel("~/R_files/data/texasPopCounty.xlsx", 
    sheet = "2010", col_types = c("blank", 
        "numeric", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
```
##helperFunctins
countypop <- gives 2010-2017 data on county
plotAll <- plots all of county stats on graph






```{r anderson, echo=FALSE}
countypop <- function(countyName){
  POP <- c(tp2010$Total[which(tp2010$`County Name` == countyName)],
  tp2011$Total[which(tp2011$`County Name` == countyName)],
  tp2012$Total[which(tp2012$`County Name` == countyName)],
  tp2013$Total[which(tp2013$`County Name` == countyName)],
  tp2014$Total[which(tp2014$`County Name` == countyName)],
  tp2015$Total[which(tp2015$`County Name` == countyName)],
  tp2016$Total[which(tp2016$`County Name` == countyName)],
  tp2017$Total[which(tp2017$`County Name` == countyName)])
  
  Anglo <- c(tp2010$Anglo[which(tp2010$`County Name` == countyName)],
  tp2011$Anglo[which(tp2011$`County Name` == countyName)],
  tp2012$Anglo[which(tp2012$`County Name` == countyName)],
  tp2013$Anglo[which(tp2013$`County Name` == countyName)],
  tp2014$Anglo[which(tp2014$`County Name` == countyName)],
  tp2015$Anglo[which(tp2015$`County Name` == countyName)],
  tp2016$Anglo[which(tp2016$`County Name` == countyName)],
  tp2017$Anglo[which(tp2017$`County Name` == countyName)])

  Black <- c(tp2010$Black[which(tp2010$`County Name` == countyName)],
  tp2011$Black[which(tp2011$`County Name` == countyName)],
  tp2012$Black[which(tp2012$`County Name` == countyName)],
  tp2013$Black[which(tp2013$`County Name` == countyName)],
  tp2014$Black[which(tp2014$`County Name` == countyName)],
  tp2015$Black[which(tp2015$`County Name` == countyName)],
  tp2016$Black[which(tp2016$`County Name` == countyName)],
  tp2017$Black[which(tp2017$`County Name` == countyName)])

  Hispanic <- c(tp2010$Hispanic[which(tp2010$`County Name` == countyName)],
  tp2011$Hispanic[which(tp2011$`County Name` == countyName)],
  tp2012$Hispanic[which(tp2012$`County Name` == countyName)],
  tp2013$Hispanic[which(tp2013$`County Name` == countyName)],
  tp2014$Hispanic[which(tp2014$`County Name` == countyName)],
  tp2015$Hispanic[which(tp2015$`County Name` == countyName)],
  tp2016$Hispanic[which(tp2016$`County Name` == countyName)],
  tp2017$Hispanic[which(tp2017$`County Name` == countyName)])

  Other <- c(tp2010$Other[which(tp2010$`County Name` == countyName)],
  tp2011$Other[which(tp2011$`County Name` == countyName)],
  tp2012$Other[which(tp2012$`County Name` == countyName)],
  tp2013$Other[which(tp2013$`County Name` == countyName)],
  tp2014$Other[which(tp2014$`County Name` == countyName)],
  tp2015$Other[which(tp2015$`County Name` == countyName)],
  tp2016$Other[which(tp2016$`County Name` == countyName)],
  tp2017$Other[which(tp2017$`County Name` == countyName)])


  year = 2010:2017
  
  
  return(data.frame(year,POP,Anglo,Black,Hispanic,Other)) 
  
}


plotAll <- function(df,name){
  d <- melt(df, id.vars="year")
  # Everything on the same plot
  ggplot(d, aes(year,value, col=variable)) + 
  geom_point() + 
  labs(title=name, x="Year", y="Population")
}




```


## Anderson county growth over 10-17

```{r Anderson}
AndersonDF <- countypop('Anderson')

summary(AndersonDF)
plotAll(AndersonDF,'Anderson')

# Separate plots
#ggplot(d, aes(year,value)) + 
#  geom_point() + 
#  stat_smooth() +
#  facet_wrap(~variable)
```

##county with largest change
We can find that harris county has the largest growth of any county. this is probably atributed to it being one of the largest. its biggest demographic growth is hispanic.

```{r bigestChange, fig.width = 10, fig.height=4}
largestChangeCounty = 1
countyNum = 1
while(countyNum <nrow(tp2010)){
  if((tp2017$Total[countyNum]-tp2010$Total[countyNum]) > (tp2017$Total[largestChangeCounty]-tp2010$Total[largestChangeCounty])){
    largestChangeCounty = countyNum
  }
  countyNum = countyNum +1
}

largestChangeCounty



largestName <- tp2010$`County Name`[which(tp2010$County == largestChangeCounty)]
DF101 <- countypop(largestName)


p1 <- plotAll(DF101,largestName)
p2 <- plotAll(DF101[,-2],largestName)
grid.arrange(p1, p2, ncol=2)


```



##predict the pop growth for Texas
While the website had the full pop data i decided just to calculate it since i have a computer that can do several million calculations a second and this is about 3000 lines.
```{r predictHarris}
my.list <- list(tp2010, tp2011,tp2012,tp2013,tp2014,tp2015,tp2016,tp2017)
year = 2010:2017
population = c(sum(tp2010$Total),sum(tp2011$Total),sum(tp2012$Total),sum(tp2013$Total),sum(tp2014$Total),sum(tp2015$Total),sum(tp2016$Total),sum(tp2017$Total))
texaspop <- data.frame(year,population)

lm1 <- lm(population~year, data=texaspop)
plotAll(texaspop,"Texas")

```







